%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2024 Joel Weinberger
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ydnt, maxbibnames=10]{biblatex}
%\usepackage[style=authortitle,sorting=ydnt, maxbibnames=10]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Joel H. W. Weinberger} \\[7.5pt]
%\href{https://github.com/username}{\raisebox{-0.05\height}\faGithub\ username} \ $|$ \ 
\href{https://www.linkedin.com/in/joelweinberger/}{\raisebox{-0.05\height}\faLinkedin\ joelweinberger} \ $|$ \ 
\href{https://www.joelweinberger.us}{\raisebox{-0.05\height}\faGlobe \ joelweinberger.com} \ $|$ \ 
\href{mailto:jww@joelweinberger.us}{\raisebox{-0.05\height}\faEnvelope \ jww@joelweinberger.com} \ %$|$ \ 
%\href{tel:+000000000000}{\raisebox{-0.05\height}\faMobile \ +00.00.000.000} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
%\section{Summary}
%This CV can also be automatically complied and published using GitHub Actions. For details, %\href{https://github.com/jitinnair1/autoCV}{click here}.
\section{Summary}
Security and software engineer and manager. Technical leader in security engineering and backend engineering. Experience building multiple teams from the ground up with high execution and output.

%Experience
\section{Professional Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Anthropic \it{Member of Technical Staff}} & \hfill October 2025 - Present \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Security engineering on the Developer Security team. Focusing on supply chain, build, and deploy security for one of the leading AI research labs.}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Lightspark \it{Head of Security Engineering}} & \hfill May 2024 - October 2025 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{First security engineer and manager for fintech startup focusing on making financial transactions as fast and cheap as possible. Led core infrastructure, application, and corp security. Designed and built the security team from the ground up, making first additional security hires.}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Snap \it{Security Engineering Manager and Technical Lead}} & \hfill Jan 2017 - Feb 2024 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Security engineering manager at Snap leading supply chain security infrastructure. Focused on hardening of dependency management, the CI/CD tool chain, and sandboxing of untrusted code. Previously managed and led Snap's secrets management program. Prior to that, was a tech lead on the Application Security Team.}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Google \it{Software Engineer}} & \hfill Feb 2013 - Jan 2017 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
Software engineer on the Chrome web browser security team. Focused on new features to enhance security
for users. Built tools for both the client and server to utilize to help developers write more secure
web applications, such as designing and implementing the Subresource Integrity (SRI) web feature and many parts of Content Security Policy.
%\begin{minipage}[t]{\linewidth}
    %\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        %\item[--] long long line of blah blah that will wrap when the table fills the column width
        %\item[--] again, long long line of blah blah that will wrap when the table fills the column width %but this time even more long long line of blah blah. again, long long line of blah blah that will %wrap when the table fills the column width but this time even more long long line of blah blah
    %\end{itemize}
    %\end{minipage}
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Coverity \it{Security Research Internship}} & \hfill Jun 2012 - Aug 2012 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
Research intern in the office of the CTO working on security technology research. Focused on next-generation analysis of
Web applications. In particular, looked at ways to connect server static analysis with client analysis
to try to find new sets of Web application vulnerabilities.
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Microsoft Research \it{Security and PL Research Internship}} & \hfill Jun 2011 - Aug 2011 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
Intern in the Research in Software Engineering (RiSE) group, working with Juan Chen, Ben Livshits,
and Nikhil Swamy. Focused on type checking of JavaScript using F*, an F]-like language with dependent and refinement typing. Worked on statically enforcing complex security policies on Web applications through the type system, focusing on browser extensions. Built a compiler from JavaScript
to F* and worked on type checking on resulting code for correctness and security properties.
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Sun Microsystems \it{Software Engineer}} & \hfill Jul 2007 - Jul 2008 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
Full-time software engineer in the Fishworks advanced development team on Sun Storage 7000 NAS
products. Worked on iSCSI and FTP integration, clustering interface support, and appliance stack
management. Worked on operating system, application, and AJAX Web development.
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{VMware \it{Software Engineer Internship}} & \hfill Jun 2006 - Aug 2006 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
Intern in the VMware ESX Core Kernel group. Developed shared memory infrastructure and signal
handling capabilities.
}
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2008 - 2012 & Ph.D., Computer Science at \textbf{University of California, Berkeley} \hfill \normalsize Thesis: Analysis and Enforcement of Web Application Security Policies, advised by Dawn Song \\

2003 - 2007 & Bachelor's and Master's Degrees at \textbf{Brown University} \\ 

\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Refereed Publications}
\begin{refsection}[refereed-citations.bib]
\nocite{*}
\printbibliography[heading=none]
\end{refsection}

\section{Technical Reports}
\begin{refsection}[tr-citations.bib]
\nocite{*}
\printbibliography[heading=none]
\end{refsection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\section{Technical Skills}
Product Security, Infrastructure Security, Application Security, and Backend Software Engineering.

Core languages: Go, Java, Python, C++, C. Proficient languages: JavaScript.

\section{Interests}
Running, reading, skiing (alpine and water), tap dancing, rock climbing, history, video games, and spending as much time as possible with his wife and three children.

Served from 2021 to 2025 as an elected at-large representative in the South Robertson Neighborhoods Council (\href{https://www.soronc.org}{soronc.org}) within the Los Angeles Neighborhoods Council system.

\end{document}
